---
title: "randomforest"
author: "Satindra Kathania"
date: "12/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# works best for both classification and regression
# create a model to predict mortality caused by heart failure
# loading the libraries
```{r,message=FALSE}
library(caret) # splitting the data
library(randomForest)
library(tidyverse)
```

# loading the data
```{r}
# USE CASE: weather prediction-play or not,Banking,Credit Risk Detection, Movie recommendation, medicine;identification of a trisk patients,Land Use,Customer Churn,Marketing

data <- readr::read_csv("heart_failure_clinical_records_dataset.csv")

glimpse(data)

summary(data)
```
# check for na
```{r}
colSums(is.na(data))
```
# convert columns to factors
```{r}
cols <- c("anaemia","diabetes","high_blood_pressure","sex","smoking","DEATH_EVENT")

data <- data %>%
  mutate_at(cols, list(~factor(.)))
glimpse(data)
```
# normalize the numeric variables
```{r}
cols2 <- c("age","creatinine_phosphokinase","ejection_fraction","platelets",
           "serum_creatinine","serum_sodium","time")

data <- data %>%
  mutate_at(cols2, list(~BBmisc::normalize(.)))

glimpse(data)
```

# visualization
# you can do visualization

# modeling
# data splitting
```{r}
index <- createDataPartition(data$DEATH_EVENT, list = FALSE, p = 0.75)

# train data
train <- data[index,]
test <- data[-index,]
```
#findind the best tree numbers(mtry)
```{r}
# bestmtry<-tuneRF(train,train$DEATH_EVENT,stepFactor = 1.2,improve=0.01,trace=T,plot=T)

```
# method 1
```{r}
model <- randomForest(DEATH_EVENT~., data = train, importance = TRUE)
model


model3 <- randomForest(DEATH_EVENT~ejection_fraction+serum_creatinine+time, data = train, importance = TRUE)
model3
```
# variable importance
```{r}
varImpPlot(model)

importance(model)
```
# making predictions
```{r}
pred <- predict(model3, newdata = test, type = "response")

# confusion table
ct <- table(pred, test$DEATH_EVENT)

# confusion matrix
cm <- confusionMatrix(ct)
cm
```

# method 2
# cross validation
```{r}
model2 <- train(DEATH_EVENT~., data=train, method="rf")
model2
```
# predictions
```{r}
pred2 <- predict(model2, newdata = test, type = "raw")

# confusion table
ct1 <- table(pred2, test$DEATH_EVENT)

# matrix
confusionMatrix(ct1)
```













