---
title: "KNN"
author: "Satindra Kathania"
date: "12/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load the libraries
```{r}
library(caret) # splitting the data, modelling
library(class) # normal knn
```
# load the data
```{r}
#USECASE:Book Recommendation,credit_data.csv,heart_dataset.csv
data(iris)
View(iris)
```
str(iris)

dplyr::glimpse(iris)

# visualization

# normalize

# scaling

#  data splitting
```{r}
set.seed(234) # reproducibility
index <- createDataPartition(iris$Species, list = F, p = 0.7)

# train data split
train <- iris[index,]

# test data split
test <- iris[-index,]
```

#balanced response 
```{r}
table(train$Species)

table(test$Species)
```
# model
```{r}
model <- knn(train = train[,-5], test = test[,-5], cl = train$Species, k = 3)
model

# confusion matrix
cm <- table(test$Species, model)
cm

confusionMatrix(cm)
```
# misclassification error
```{r}
shipunov::Misclass(test$Species, model)
```
# methods, names(getModelInfo())
# using caret
```{r}
model2 <- train(Species ~., data=train, method="knn")
model2
```
# predictions
```{r}
pred <- predict(model2,newdata = test)

# classification table
ct <- table(test$Species, pred)
ct

confusionMatrix(ct)
```
shipunov::Misclass(test$Species, pred)



Normalization
normalize<-function(x){
return((x-min(x)/max(x)-min(x))) 
}

loan.subset.n<-as.data.frame(lapply(loan.subset[,2:8],normalize))


