---
title: "Predict wine quality using SVM"
author: "Satindra Kathania"
date: "12/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading the data and packages

    We are going to predict the red wine quality using svm. this is going to be classification problem, if the quality of wine is >= 7 we are going to classify as good quality else bad.
    
```{r data and packages}
library(tidyverse)
library(caret)
library(DataExplorer) # plotting the missing data
```
# reading the data
```{r,`show_col_types = FALSE`}
wine_quality <- read_csv('data/winequality-red.csv')
summary(wine_quality)
str(wine_quality)
```

## Analysis eg NA ...

```{r Analysis}
# handling NA values
colSums(is.na(wine_quality))# no NA values
# plotting NA values
plot_missing(wine_quality)
```

## Exploratory Data Analysis

```{r EDA}
# plotting individual variables
# alcohol
# skewed
ggplot(data = wine_quality) +
  geom_histogram(aes(alcohol), bins = 20) +
  ggtitle('distribution of alcohol')

# density plot
ggplot(data = wine_quality) +
  geom_density(aes(x=alcohol))

ggplot(data = wine_quality) +
  geom_histogram(aes(log(alcohol)), bins = 20) 

# sulphates
ggplot(data = wine_quality) +
  geom_histogram(aes(sulphates), bins = 20)
# pH
ggplot(data = wine_quality) +
  geom_histogram(aes(pH), bins = 20)
# density
ggplot(data = wine_quality) +
  geom_histogram(aes(density), bins = 20)
# total sulfur dioxide
ggplot(data = wine_quality) +
  geom_histogram(aes(`total sulfur dioxide`), bins = 20)
# free sulfur dioxide
ggplot(data = wine_quality) +
  geom_histogram(aes(`free sulfur dioxide`), bins = 20)
# chlorides
ggplot(data = wine_quality) +
  geom_histogram(aes(chlorides), bins = 20)
# residual sugar
ggplot(data = wine_quality) +
  geom_histogram(aes(`residual sugar`), bins = 20)
# citric acid
ggplot(data = wine_quality) +
  geom_histogram(aes(`citric acid`), bins = 20)
# volatile acidity
ggplot(data = wine_quality) +
  geom_histogram(aes(`volatile acidity`), bins = 20)
# fixed acidity
ggplot(data = wine_quality) +
  geom_histogram(aes(`fixed acidity`), bins = 20)

## box plot
# outliers
ggplot(data = wine_quality)+
  geom_boxplot(aes(y=`fixed acidity`))

# most of these variables are skewed.
# we will fit the model as it is and the you will transform them later 
# on to see the effect
# try experimenting on your own, for the sake of this video i will not
```

```{r}
library(corrplot)
cr<-cor(wine_quality)
corrplot(cr,type="lower")
```


# converting the quality variable into categorical
```{r}
wine_quality$quality <- as.factor(wine_quality$quality)
```

## Data Splitting

```{r data splitting}
# splitting the data
# train 75% and test 25%
index <- createDataPartition(wine_quality$quality, p=0.75, list = FALSE)
train <- wine_quality[index,]
test <- wine_quality[-index,]
```

## modelling

```{r model1}
# names(getModelInfo()), gives a list of the methods you can use
library(kernlab)

grid<-expand.grid(C=c(0.5,1,1.25,1.50,1.75,2,5),sigma=c(.05,.09,0.1))


svm_radial <- train(quality~., data=train, 
                preProcess=c("scale","center"),
                tuneGrid=grid,
                method='svmRadial')
svm_radial
```

# making the predictions
```{r}
pred1 <- predict(svm_radial, newdata = test)
pred1
confusionMatrix(table(pred1,test$quality))
```

```{r}
#trctrl<-trainControl(method = "repeatedcv",number = 10,repeats = 3)
grid<-expand.grid(C=c(0.5,1,1.25,1.50,1.75,2,5))
svm_linear<-train(quality~., data=train, 
                  #trControl=trctrl,
                preProcess=c("scale","center"),
                 tuneGrid=grid,
                method='svmLinear')
svm_linear

pred_L <- predict(svm_linear, newdata = test)
#pred_L
confusionMatrix(table(pred_L,test$quality))
```


```{r}
#trctrl<-trainControl(method = "repeatedcv",number = 10,repeats = 3)
svm_Poly<-train(quality~., data=train, 
                  #trControl=trctrl,
                preProcess=c("scale","center"),
                method='svmPoly')
svm_Poly
pred1 <- predict(svm_radial, newdata = test)
pred1
confusionMatrix(table(pred1,test$quality))

```

```{r}
#trctrl<-trainControl(method = "repeatedcv",number = 10,repeats = 3)

grid<-expand.grid(C=c(0.5,1,1.25,1.50,1.75,2,5),sigma=c(.05,.09,0.15,0.2))
svm_RadialSigma<-train(quality~., data=train, 
                  #trControl=trctrl,
                preProcess=c("scale","center"),
                method='svmRadialSigma')
svm_RadialSigma

pred_RadialSigma <- predict(svm_RadialSigma, newdata = test)
#pred_RadialSigma
confusionMatrix(table(pred_RadialSigma,test$quality))
```



# To compare predicted values and actual values, we can use plots for continious values
```{r}
plot(test$quality,type="l",lty=1.8,col="red")
lines(pred1,type="l",col="blue")

plot(svm_linear)
plot(svm_radial)
plot(svm_RadialSigma)
plot(svm_Poly)
```



## you can improve the model by handling the skewed variables and the outliers.

# Null Deviance shows how well the response variable is predicted by a model that includes only the intercept(grand mean)

# Residual deviance shows how well the response variable is predicted with inclusion of independent variables.

# AIC should be smaller

# ROC curve: for calculating the accuracy of our model


res<-predict(model,testing,type="response")
table(ActualValue=training$type,PredictedValue=res>0.5)
or 
table(ActualValue=training$type,PredictedValue=res>0.3)



res<-predict(model,training,type="response")
library(ROCR)
ROCRPred=prediction(res,training,type="response)
ROCRPref<-performance(ROCRPred,"tpr","fpr")
plot(ROCRPref,colorize=TRUE,print.cutoff.at=seq(0.1,by=0.1))

#Finding multicollinearity
Variance inflation factor(VIF):measures the increase in the variance (the square of the estimates standard devuations) of an estimated regression coefficient due to multicollinearity.

# vif
install.packages("car")
library(car)
model<-lm(medv~. ,data=training_data)
vif(model)
A VIF of 1 means that there is no correlation amomg variables.

attach(Boston)
library(lattice)
splom(~Boston[c(1:6,14)]),groups=NULL,data=Boston,axis.line.tck=0,axis.text.alpha=0)
splom(~Boston[c(7:14)]),groups=NULL,data=Boston,axis.line.tck=0,axis.text.alpha=0)

library(corrplot)
cr<-cor(wine_quality)
corrplot(cr,type="lower")
corrplot(cr,type="number")







 thanks for watching.